Molecular Gas \old{Dynamics} \new{Kinematics and Spectral Energy Distribution Properties} of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-12-08 WRITEUP/diff.tex
after proof-reading by myself, will give to DR

\subsection{PdBI \bco}
\old{Observations of the \mbox{\bco} rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
at the $\nu_{\rm LO}$\eq139.256\,GHz
were carried out using IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.}
\new{Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
towards RXJ1131
were carried out using IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
Riechers).
Based on the CARMA \cco line redshift of $z_{\rm CO(3-2)}$\eq0.655,
the \bco line is redshifted to $\nu_{\rm obs}$\eq139.256\,GHz.
}
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

\begin{figure}[!htbp]
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
\old{\mbox{The velocity scale is with respect to $z$=0.6537, which corresponds to the
dynamical center of the \bco line.}}\new{\mbox{The velocity scale is the same as in \Fig{CO21spec}.}} The spectral resolution for \cco and \bco
is 36 \kms and 22 \kms, respectively.
\label{fig:co32spec}}
\end{figure}

@@

We detect \old{2\,mm}\new{2.2\,mm} continuum emission at an
integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}). Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the visibility-plane to remove the unresolved part of the
emission, which we here assume to be dominated by the foreground galaxy. 
\old{The peak flux (0.39\,$\pm$\,0.08\,mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_{\nu}$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission towards
the background galaxy (RXJ1131).
The quoted uncertainty is from the flux measurement in the residual map and does not account for that in the de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.}
\new{The emission
in the residual map coincides spatially with the lensed arc. We measure a flux density 
of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy for this residual component.
This flux density is consistent with
the difference between the integrated and the peak flux density measured in the
original continuum map ($\sim$0.4 mJy). 
We therefore adopt $S_{\nu}$\eq0.39\pmm0.12 mJy as the best estimate for the 2\,mm continuum flux of 
the background galaxy (RXJ1131). 
We here quote a conservative uncertainty, which is derived by adding those associated with the flux density of the 
point-source model ($\delta S_{\nu}$\eq0.088\,mJy) and 
the peak flux in the residual map (0.08\,mJy) 
in quadrature. We caution that this does not account for that in the 
de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.}
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.

@@

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and the core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc with their centroids
coincident with the optical emission from the quasar.
We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
\old{We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.024
for the foreground
galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.345
for the background galaxy by fitting a
power-law ($S_\nu \propto \nu^{\alpha}$) to the continuum emission at
5\,GHz and 2\,mm.}
\new{We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.02\pmm0.07
for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.35\pmm0.21 % differential
for the background galaxy by fitting
power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum fluxes at
5\,GHz and 2\,mm. 
The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \mbox{\citep[$\alpha$\ssim$-$0.7; e.g.,][]{Andreani93a}}. This likely suggests % {\bf DR: 3C273 flat-spectrum radio source BLAH}
that a fraction of the observed 2\,mm emission arises from thermal dust  emission. 
This spectral slope would be even shallower 
if the background source contributes to the unresolved fraction of the
2\,mm flux. This would also 
explain the flat spectrum found for the foreground galaxy, which is atypical of elliptical galaxies. 
Assuming a synchrotron slope of $\alpha$\ssim$-$0.7, we would expect
a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm
and thus a flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy relative to this expectation
likely arises due to thermal dust emission.
}

@@

A better fit is found for the lens model of
the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet[hereafter B08]{Brewer08a}, who find an optically faint companion
(component F in their paper) $\sim$2.4\,kpc in projection from the AGN host galaxy in $V$-band,
and with \citetalias{Claeskens06a}, who find evidence for an interacting galaxy near RXJ1131.
Spatially, the red velocity component of the CO emission
also coincides with this component F. It is therefore likely that we
detect \bco emission in a companion galaxy.
\defcitealias{Brewer08a}{B08}

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[width=1.0\textwidth]{../Figures/co_channel_maps.eps}
\caption{
Channel maps of the PdBI \bco data cube toward RXJ1131 at 22\,\kms resolution.
Black crosses indicate the positions of the lensed knots (AGN emission,
which correspond to components ABCD in \citetalias{Claeskens06a}). The central white-filled
star indicates the position of the foreground lensing galaxy (component G
in \citetalias{Claeskens06a}).
Central velocities are shown at the top of each map.
Contours start and increment in steps of
$\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
\end{figure*}

@@

\old{Similar to previous studies of RXJ1131, where
differential lensing across the {\it HST}
$V$-, $I$-, and $H$-bands has been detected with a
magnification factor decreasing from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}},
the highly asymmetric \mbox{\bco} line profile suggests that
differential lensing is also non-negligible for CO,
causing the redshifted emission to be apparently much brighter than the
blueshifted component.
This can be explained by the difference in magnification factor $(\mu_{\rm L})$ which
varies from 8.7 to 3.1 across the \mbox{\bco} line (\mbox{\Tab{model}}) and also partly due to a contribution from the companion in the redshifted velocity channels.}
\new{Previous studies of RXJ1131 find evidence for differential lensing across 
the {\it HST} $V$-, $I$-, and $H$-bands, where the
magnification factor varies from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}}.
This indicates that the spatial positions and extents of different stellar populations 
within the host galaxy are dissimilar with respect to the caustic which may be a result of dust extinction and reddening.
The best-fit lens models obtained here for different CO channel slices show that differential lensing also plays 
an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
from 8.7 to 3.1 across different kinematic components (\mbox{\Tab{model}}).
The asymmetry in the line profile is therefore predominantly a result of differential lensing, where 
the redshifted CO-emitting gas is only apparently much brighter than the
blueshifted component due to a higher magnification factor.
A secondary effect is likely a result of including emission from the companion in the most redshifted velocity channels.}
The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
positions relative to the caustics in \Fig{model}, where the red wing
emission mainly originates near the cusp
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
are $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the symmetric source-plane
velocity gradient in our lens model (\Fig{model} and \Fig{PV}).

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[trim=0 0 30 0, clip, width=0.4\textwidth]{../Figures/veloGradient_markers}
\includegraphics[width=0.525\textwidth]{../Figures/bestfit_PV.eps}
\caption{\old{Left: Source-plane positions from best-fit \mbox{\bco} lens models are indicated with their associated uncertainties atop
the observed first moment map. The contours are at steps of 50\,\kms.
Right: PV slice along the major axis in the source plane at PA\,=\,121\degr.
Dashed line shows the best-fit ``rotation curve'' using an arctangent model.}
%
\new{Velocity gradient of the \mbox{\bco} emission observed in RXJ1131 and the de-lensed velocity gradient obtained from lens modeling.
Left: source-plane positions obtained from the best-fit lens models (presented in \mbox{\Sec{lensmodel}}) are shown 
as markers color-coded by their velocities
atop the observed first moment map (i.e., in the image-plane; see \mbox{\Fig{CO21mom}}). 
The contours are in steps of 50\,\kms. 
Despite the distorted first moment map in the image-plane due to differential lensing and beam smearing effects, the source-plane velocity gradient reconstructed from dynamical lens modeling suggests that
RXJ1131 is intrinsically a kinematically-ordered disk.
Right: PV slice extracted along the fitted major axis at PA\,=\,121\degr based on 
the reconstructed source-plane velocity gradient.}
The vertical error bars show the channel width for
each model and the horizontal error bars are the
1$\sigma$ uncertainties on the source-plane positions \new{along the major axis}.
\label{fig:PV}}
\end{figure*}

@@

We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\old{\eq19\pmm5\%}\new{\eq18\pmm4\%}
and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M^*$)\old{\mbox{\eq32\petm{7}{12}\% for RXJ1131.}} \new{\mbox{\eq34\pmm16\%} for the merger system (i.e., RXJ1131 and companion).}
Recent studies find that the baryonic gas fraction of starburst galaxies has decreased from $f_{\rm mol}$\ssim40\% to $\lesssim$10\% between $z$\ssim2 and $z$\ssim0 \citep[\citetalias{Solomon97a};][]{GS04a, Tacconi06a},
and from $f_\textrm{mol}$\ssim50\% to $\sim$5\% between the same redshift range for
``normal'' star-forming galaxies \citep{Geach11a, Saintonge11a, Tacconi13a}\footnote{These authors use the ``Galactic'' value of
\alphaco\eq4.6\,\alphaU to compute the molecular gas mass.}.
Both the dynamical and baryonic gas mass fractions of RXJ1131+companion are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2
which has been suggested as the cause for the decline in sSFR and cosmic \SF history towards $z$\ssim0 \citep[e.g.,][]{Tacconi13a,CW13,Genzel15a}.

@@

\old{Alternatively, large velocity offsets between emission lines of the
BLR and the NLR may arise in a recoiling black hole (BH),
where its BLR is moving at high velocity relative to the bulk of its host galaxy
\mbox{\citep{Madau04a, Bonning07a, Loeb07a}}.}
\old{A recoiling black hole is expected
when a pair of uneven mass BH coalesce, during which their orbital energy is being released
as gravitational wave and a
non-zero net angular momentum is being carried away.
Depending on their initial conditions, numerical relativity simulations have shown that
the recoil velocity can reach up to \mbox{$\sim$4000\,\kms for} }
\old{spinning BHs \mbox{\citep[e.g.,][]{Campanelli07a}}.}
\old{Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \mbox{\citep{Civano10a}} and
SDSS 0956+5127 at $z$\,$\sim$\,0.714 \mbox{\citep{Steinhardt12a}}.
One notable system is SDSSJ0927+2943 at $z$\,$\sim$\,0.713, where
a set of redshifted narrow lines and a second set of blueshifted broad AGN lines
have been observed \mbox{\citep{Komossa08a}},  similar to the case for RXJ1131.
However, this scenario was recently refuted by \mbox{\citet{Decarli14a}}, who confirm that the
BLR lines in SDSSJ0927+2943 are consistent with the CO systemic redshift.} 
\new{The observed velocity offset between the BLR and NLR lines may be explained by
a recoiling black hole (BH), 
where the BLR is moving at high velocity relative to the bulk of its host galaxy
\mbox{\citep{Madau04a, Bonning07a, Loeb07a}}.}
\new{A recoiling black hole is expected
when a pair of uneven mass BH coalesce, during which their orbital energy is being released
as gravitational wave and a non-zero net angular momentum is being carried away.
Depending on their initial conditions (e.g., black hole mass ratio, spin-orbit orientation, spin magnitude), 
numerical relativity simulations have shown that recoil velocities can reach up to }
\new{\mbox{$v_{\rm kick}$\ssim4000\,\kms} for spinning BHs, 
with typical recoil velocities of \mbox{$v_{\rm kick}$\ssim100\,$-$\,500\,\kms }}
\new{\mbox{\citep[\eg][]{Libeskind06a,Campanelli07a}}.}
\new{Several sources have been proposed as recoiling BH candidates} 
\new{\mbox{\citep[][]{Komossa08a, Civano10a, Steinhardt12a}}}.
% For the candidate SDSS J0927+2943 at $z$\,$\sim$\,0.713 \citep{Komossa08a}, }
\new{However, \mbox{\citet{Decarli14a}} have recently refuted 
such scenario for one of the candidates --- SDSS J0927+2943 --- by finding that the redshift of its
BLR lines is indeed consistent with its CO systemic redshift.
}
This is in contrast with RXJ1131, where our CO observations confirm the \old{blueshifted}\new{redshifted} BLR.
\old{Since this model requires a merged BH, it would imply that RXJ1131 might
have been in a previous merger, which would also} 
\new{Since this scenario requires a coalesced BH, it would imply that RXJ1131 
is a product of previous merger, which is not implausible and 
might also} explain the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.

@@

\subsection{The $M_{\rm BH}$$-$\mbulge Relation}
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{0.11}{0.08}\%
using the black hole mass of $M_{\rm BH}$\ssim8\E{7}\,\Msun \citep{Sluse12a}
and the stellar mass derived in \Sec{SED} as an upper limit to the bulge mass.
This ratio is consistent with those of other intermediate-$z$ radio-loud AGNs \citep{McLure06a}
but is higher than those of nearby AGNs \citep{HR04a}, supporting
the emerging picture that quasars
grow faster and/or earlier than their host galaxies at higher redshifts \citep[e.g., ][]{Walter04a, Peng06a, McLure06a,Riechers08a}.
The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of RXJ1131 compared to local AGNs
suggests that the bulk of the black hole mass of RXJ1131 is largely in place while its stellar bulge is still assembling.

>>>>

\subsection{PdBI \bco}
\old{Observations of the \mbox{\bco} rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
at the $\nu_{\rm LO}$\eq139.256\,GHz
were carried out using IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
Riechers).} 
\new{Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
towards RXJ1131
were carried out using IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
Riechers).
Based on the CARMA \cco line redshift of $z_{\rm CO(3-2)}$\eq0.655,
the \bco line is redshifted to $\nu_{\rm obs}$\eq139.256\,GHz.}
Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

\begin{figure}[!htbp]
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
\old{The velocity scale is with respect to $z$=0.6537, which corresponds to the
dynamical center of the \mbox{\bco} line.} \new{The velocity scale is the same as in \mbox{\Fig{CO21spec}.}} The spectral resolution for \cco and \bco
is 36 \kms and 22 \kms, respectively.
\label{fig:co32spec}}
\end{figure}

@@

We detect \old{2\,mm}\new{2.2\,mm} continuum emission at an
integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}). Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the visibility-plane to remove the unresolved part of the
emission, which we here assume to be dominated by the foreground galaxy. 
\old{The peak flux (0.39\,$\pm$\,0.08\,mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_{\nu}$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission towards
the background galaxy (RXJ1131).
The quoted uncertainty is from the flux measurement in the residual map and does not account for that in the de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.}
\new{The emission
in the residual map coincides spatially with the lensed arc. We measure a flux density 
of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy for this residual component.
This flux density is consistent with
the difference between the integrated and the peak flux density measured in the
original continuum map ($\sim$0.4 mJy). 
We therefore adopt $S_{\nu}$\eq0.39\pmm0.12 mJy as the best estimate for the 2\,mm continuum flux of 
the background galaxy (RXJ1131). 
We here quote a conservative error bar, which is derived by adding the uncertainty 
associated with the flux density of the 
point-source model ($\delta S_{\nu}$\eq0.088\,mJy) with
that of the peak flux in the residual map (0.08\,mJy) 
in quadrature. We caution that this does not account for the systematic uncertainties of the 
de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.}
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.

@@

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and the core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc with their centroids
coincident with the optical emission from the quasar.
We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
\old{We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.024
for the foreground
galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.345
for the background galaxy by fitting a
power-law ($S_\nu \propto \nu^{\alpha}$) to the continuum emission at
5\,GHz and 2\,mm.}
\new{We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.02\pmm0.07
for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.35\pmm0.21 % differential
for the background galaxy by fitting
power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum fluxes at
5\,GHz and 2\,mm. 
The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \mbox{\citep[$\alpha$\ssim$-$0.7; e.g.,][]{Andreani93a}}. This likely suggests % {\bf DR: 3C273 flat-spectrum radio source BLAH}
that a fraction of the observed 2\,mm emission arises from thermal dust  emission. 
This spectral slope would be even shallower 
if the background source contributes to the unresolved fraction of the
2\,mm flux. This would also 
explain the flat spectrum found for the foreground galaxy, which is atypical of elliptical galaxies. 
Assuming a synchrotron slope of $\alpha$\ssim$-$0.7, we would expect
a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm
and thus an excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy relative to this expectation
likely arises due to thermal dust emission.
}

@@

A better fit is found for the lens model of
the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet[hereafter B08]{Brewer08a}, who find an optically faint companion
(component F in their paper) $\sim$2.4\,kpc in projection from the AGN host galaxy in $V$-band,
and with \citetalias{Claeskens06a}, who find evidence for an interacting galaxy near RXJ1131.
Spatially, the red velocity component of the CO emission
also consistent with this component F. It is therefore likely that we
detect \bco emission in a companion galaxy.
\defcitealias{Brewer08a}{B08}

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[width=1.0\textwidth]{../Figures/co_channel_maps.eps}
\caption{
Channel maps of the PdBI \bco data at 22\,\kms resolution.
Black crosses indicate the positions of the lensed knots (AGN emission,
which correspond to components ABCD in \citetalias{Claeskens06a}). The white-filled
star indicates the position of the foreground lensing galaxy (component G
in \citetalias{Claeskens06a}).
Central velocities are shown at the top of each map.
Contours start and increment in steps of
$\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
\end{figure*}

@@

\old{Similar to previous studies of RXJ1131, where
differential lensing across the {\it HST}
$V$-, $I$-, and $H$-bands has been detected with a
magnification factor decreasing from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}},
the highly asymmetric \mbox{\bco} line profile suggests that
differential lensing is also non-negligible for CO,
causing the redshifted emission to be apparently much brighter than the
blueshifted component.
This can be explained by the difference in magnification factor $(\mu_{\rm L})$ which
varies from 8.7 to 3.1 across the \mbox{\bco} line (\mbox{\Tab{model}}) and also partly due to a contribution from the companion in the redshifted velocity channels.}
\new{Previous studies of RXJ1131 find evidence for differential lensing across 
the {\it HST} $V$-, $I$-, and $H$-bands, where the
magnification factor varies from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}}.
This indicates that emission from different stellar populations 
within the host galaxy are dissimilar with respect to the caustic. 
%This imply that different stellar populations in the host galaxy are not co-spatial, and have  
%different spatial extents, or
%may be a result of dust extinction and reddening.
The best-fit lens models obtained here for different CO channels show that differential lensing also plays 
an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
from 8.7 to 3.1 across different kinematic components (\mbox{\Tab{model}}).
The asymmetry in the line profile (\Fig{CO21spec} and \Fig{delensed}) is therefore predominantly a result of
the redshifted CO-emitting gas being more strongly-magnified 
than the 
blueshifted component.
A secondary effect is likely a result of including emission from the companion in the most redshifted velocity channels.}
The variation in $\mu_{\rm L}$ found across channels is consistent with the source-plane
positions relative to the caustics in \Fig{model}, where the red wing
emission mainly originates near the cusp
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
are $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the symmetric source-plane
velocity gradient in our lens model (\Fig{model} and \Fig{PV}).

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[trim=0 0 30 0, clip, width=0.4\textwidth]{../Figures/veloGradient_markers}
\includegraphics[width=0.525\textwidth]{../Figures/bestfit_PV.eps}
\caption{\old{Left: Source-plane positions from best-fit \mbox{\bco} lens models are indicated with their associated uncertainties atop
the observed first moment map. The contours are at steps of 50\,\kms.
Right: PV slice along the major axis in the source plane at PA\,=\,121\degr.
Dashed line shows the best-fit ``rotation curve'' using an arctangent model.}
%
\new{Velocity gradient of the \mbox{\bco} emission observed in RXJ1131 and the de-lensed velocity gradient obtained from lens modeling.
Left: source-plane positions obtained from the best-fit lens models (presented in \mbox{\Sec{lensmodel}}) are shown 
as markers
atop the observed first moment map (i.e., in the image-plane; see \mbox{\Fig{CO21mom}}). 
The markers are color-coded by their centroid velocities.
The contours are in steps of 50\,\kms. 
Despite the distorted first moment map in the image-plane due to differential lensing and beam smearing effects, the source-plane velocity gradient reconstructed from dynamical lens modeling suggests that
RXJ1131 is intrinsically a kinematically-ordered disk.
Right: PV slice extracted along the fitted major axis at PA\,=\,121\degr based on 
the reconstructed source-plane velocity gradient.}
The vertical error bars show the channel width for
each model and the horizontal error bars are the
1$\sigma$ uncertainties on the source-plane positions \new{along the major axis}.
\label{fig:PV}}
\end{figure*}

@@

We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\old{\eq19\pmm5\%}\new{\eq18\pmm4\%}
and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\old{\mbox{\eq32\petm{7}{12}\% for RXJ1131.}} \new{\mbox{\eq34\pmm16\%} for the merger system (i.e., RXJ1131 and companion).}
Recent studies find that the baryonic gas fraction of starburst galaxies has decreased from $f_{\rm mol}$\ssim40\% to $\lesssim$10\% between $z$\ssim2 and $z$\ssim0 \citep[\citetalias{Solomon97a};][]{GS04a, Tacconi06a},
and from $f_\textrm{mol}$\ssim50\% to $\sim$5\% between the same redshift range for
``normal'' star-forming galaxies \citep{Geach11a, Saintonge11a, Tacconi13a}\footnote{These authors use the ``Galactic'' value of
\alphaco\eq4.6\,\alphaU to compute the molecular gas mass.}.
Both the dynamical and baryonic gas mass fractions of RXJ1131+companion are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2
which has been suggested as the cause for the decline in sSFR and cosmic \SF history towards $z$\ssim0 \citep[e.g.,][]{Tacconi13a,CW13,Genzel15a}.

@@

\old{Alternatively, large velocity offsets between emission lines of the
BLR and the NLR may arise in a recoiling black hole (BH),
where its BLR is moving at high velocity relative to the bulk of its host galaxy
\mbox{\citep{Madau04a, Bonning07a, Loeb07a}}.}
\old{A recoiling black hole is expected
when a pair of uneven mass BH coalesce, during which their orbital energy is being released
as gravitational wave and a
non-zero net angular momentum is being carried away.
Depending on their initial conditions, numerical relativity simulations have shown that
the recoil velocity can reach up to \mbox{$\sim$4000\,\kms for} }
\old{spinning BHs \mbox{\citep[e.g.,][]{Campanelli07a}}.}
\old{Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \mbox{\citep{Civano10a}} and
SDSS 0956+5127 at $z$\,$\sim$\,0.714 \mbox{\citep{Steinhardt12a}}.
One notable system is SDSSJ0927+2943 at $z$\,$\sim$\,0.713, where
a set of redshifted narrow lines and a second set of blueshifted broad AGN lines
have been observed \mbox{\citep{Komossa08a}},  similar to the case for RXJ1131.
However, this scenario was recently refuted by \mbox{\citet{Decarli14a}}, who confirm that the
BLR lines in SDSSJ0927+2943 are consistent with the CO systemic redshift.} 
\new{The observed velocity offset between the BLR and NLR lines may be explained by
a recoiling black hole (BH), 
where the BLR is moving at high velocity relative to the bulk of its host galaxy
\mbox{\citep{Madau04a, Bonning07a, Loeb07a}}.}
\new{Depending on the initial conditions of the black hole pair 
(e.g., black hole mass ratio, spin-orbit orientation, spin magnitude), 
numerical relativity simulations have shown that recoil velocities can reach up to }
\new{\mbox{$v_{\rm kick}$\ssim4000\,\kms} for spinning BHs, 
with typical recoil velocities of \mbox{$v_{\rm kick}$\ssim100\,$-$\,500\,\kms }}
\new{\mbox{\citep[\eg][]{Libeskind06a,Campanelli07a}}.}
\new{Several sources have been proposed as recoiling BH candidates} 
\new{\mbox{\citep[][]{Komossa08a, Civano10a, Steinhardt12a}}}.
% For the candidate SDSS J0927+2943 at $z$\,$\sim$\,0.713 \citep{Komossa08a}, }
\new{However, \mbox{\citet{Decarli14a}} have recently refuted 
such scenario for one of the candidates --- SDSS J0927+2943 --- by finding that the redshift of its
BLR lines is indeed consistent with its CO systemic redshift.
}
This is in contrast with RXJ1131, where our CO observations confirm the \old{blueshifted}\new{redshifted} BLR.
\old{Since this model requires a merged BH, it would imply that RXJ1131 might
have been in a previous merger, which would also} 
\new{Since this scenario requires a coalesced BH, it would imply that RXJ1131 
is a product of previous merger, which is not implausible and 
might also} explain the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.

@@

\subsection{The $M_{\rm BH}$$-$\mbulge Relation}
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{0.11}{0.08}\%
using the black hole mass of $M_{\rm BH}$\ssim8\E{7}\,\Msun \citep{Sluse12a}
and the stellar mass derived in \Sec{SED} as an upper limit to the bulge mass.
This ratio is consistent with those of other intermediate-$z$ radio-loud AGNs \citep{McLure06a}
but is higher than those of nearby AGNs \citep{HR04a}.
Our results therefore support
the emerging picture that quasars
grow faster and/or earlier than their host galaxies at higher redshifts \citep[e.g., ][]{Walter04a, Peng06a, McLure06a,Riechers08a}.
The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of RXJ1131 compared to local AGNs
suggests that the bulk of the black hole mass of RXJ1131 is largely in place while its stellar bulge is still assembling.
